---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fars

<!-- badges: start -->
[![Build Status](https://travis-ci.org/Halberdier/fars.svg?branch=master)](https://travis-ci.org/Halberdier/fars)
<!-- badges: end -->

The goal of fars is to facilitate visualization of data from the FARS, the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Halberdier/fars")
```
## Exported functions

```{r setup, echo=FALSE}
library(fars)
```

This package exports two convenient functions for visualization of data from the FARS, the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)).

### Summarizing years
The first function is `fars_summarize_years`, which gets a vector of years as argument and provides a tibble with one column per given year with the number of accidents per month, as in the following example:
```{r summarize_years}
fars_summarize_years(c(2013, 2014))
```

### Plotting accidents on a state map
The second function is `fars_map_state`. Given a US state numeric code and a year, it plots the accident locations on the state map. The states are encoded according with the Federal Information Processing Standard ([FIPS](https://en.wikipedia.org/wiki/Federal_Information_Processing_Standard_state_code)).
In the following example, Florida is shown (code 12), easily recognizable.
```{r map_state}
fars_map_state(12, 2014)
```
