---
title: "Introduction to FARS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(fars)
```

This package exports two convenient functions for visualization of data from the FARS, the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)).

## Summarizing years
The first function is `fars_summarize_years`, which gets a vector of years as argument and provides a tibble with one column per given year with the number of accidents per month, as in the following example:
```{r summarize_years}
fars_summarize_years(c(2013, 2014))
```

## Plotting accidents on a state map
The second function is `fars_map_state`. Given a US state numeric code and a year, it plots the accident locations on the state map. The states are encoded according with the Federal Information Processing Standard ([FIPS](https://en.wikipedia.org/wiki/Federal_Information_Processing_Standard_state_code)).
In the following example, Florida is shown (code 12), easily recognizable.
```{r map_state}
fars_map_state(12, 2014)
```
